Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2023-12-23 doc/manuscript/translocation_bioarxiv_SI.tex
Compile versions for journal and preprint server

\hypertarget{laboratory-methods}{%
\subsection{Laboratory Methods}\label{laboratory-methods}}

@@

The state transition matrix \(\Psi_{t, i}\) contains the probabilities
of individual \(i\) transitioning from state \(u_{i, t}\) (rows) to
\(u_{i, t+1}\) (columns) between primary period \(t\) and \(t+1\). For
unintroduced individuals which naturally recruit, this matrix is given
by:

@@

To complete the specification of the Bayesian model, we need to specify
priors for all unknown parameters. The recruitment parameter priors were
specified as follows:

@@

\hypertarget{population-viability-modeling-1}{%
\subsection{Population viability
modeling}\label{population-viability-modeling-1}}

\hypertarget{incorporating-yearly-variability-in-vital-rates}{%
\subparagraph{Incorporating yearly variability in vital
rates}\label{incorporating-yearly-variability-in-vital-rates}}

We computed yearly survival probabilities for translocated adults
\(\sigma_{A_T}\) and naturally recruited adults \(\sigma_{A_R}\) from
the posterior distribution of individual state trajectories derived from
mrmr CMR models. Although we observed yearly variability in adult
survival within a population, the magnitude of this variability was
small compared to among-population variability
(Fig. 3). Thus, we did not include
yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in
the successful recruitment of adults, greater than what we would expect
from Poisson variability around a mean value. Therefore, we allowed for
yearly variability in the probability of year 1 juvenile survival and
recruitment (additional details provided in \textbf{Estimating model
parameters} below). We also could have included environmental
stochasticity in year 2 juvenile survival and recruitment
\(\sigma_{J_2}\), but our elasticity analysis (\textbf{Supporting
Information-Population viability modeling-Model analysis and
simulation}) showed that this parameter had little effect on host growth
rate relative to \(\sigma_{J_1}\) (Figure~\ref{fig-viability-supp}).

\hypertarget{estimating-model-parameters}{%
\subparagraph{Estimating model
parameters}\label{estimating-model-parameters}}

The baseline parameter values for the model and how they were estimated
are given in Table~\ref{tbl-param_values}. Parameters \(\sigma_{A_T}\)
and \(\sigma_{A_R}\) were extracted directly from our CMR models (see
\textbf{Materials and Methods - Estimation of frog survival and
abundance} and \textbf{Supporting Information - Frog population recovery
- Estimation of frog survival and abundance} for details). For
populations where we had a sufficient number of PIT-tagged,
naturally-recruited adults, we observed that \(\sigma_{A_T}\) and
\(\sigma_{A_R}\) could be notably different, with
\(\sigma_{A_R} > \sigma_{A_T}\) (Figure~\ref{fig-compare_surv_probs}). For populations lacking sufficient numbers of naturally-recruited
adults, we were unable to directly estimate \(\sigma_{A_R}\), and
instead set \(\sigma_{A_R} = \sigma_{A_T}\).

To estimate the \(\sigma_{A_R}\), we used the posterior distribution of
predicted true states for naturally-recruited individuals (1=not
recruited, 2=alive, 3=dead, as described in \textbf{Supporting
Information-Frog population recovery-CMR model structure}), then
calculated the posterior probability of individuals surviving between
consecutive primary periods, conditional on being alive in the first
primary period (e.g., given a value of 2 (alive) in the first primary
period, how often was the value still 2 (alive) in the next primary
period compared to 3 (dead)?) . This yielded posterior distributions for
survival probabilities between primary periods. However, because the
time interval between primary periods differed, the survival
probabilities between different consecutive primary periods were not
directly comparable. To address this, we converted the survival
probabilities between each consecutive primary period to per day death
rates, propagating the uncertainty from the posterior distributions. We
then took a weighted average of these death rates, weighted by the time
interval between primary periods, to get the average per day death rate
over the entire CMR survey. We converted this per day death rate \(d\)
back to a yearly survival probability using
\(\exp(-d \times 365 \text{ days})\). We used the same procedure for
\(\sigma_{A_T}\) such that our estimates of average yearly survival
probability were comparable between \(\sigma_{A_R}\) and
\(\sigma_{A_T}\).

\hypertarget{model-analysis-and-simulation}{%
\subparagraph{Model analysis and
simulation}\label{model-analysis-and-simulation}}

We performed four analyses on our model. First, we considered a
deterministic version of our model with no yearly heterogeneity in year
1 juvenile survival and recruitment probability \(\sigma_{J_1}\), and
calculated the predicted long-run growth rate \(\lambda\) of a
population for different values of \(\sigma_{A_R}\) and
\(\sigma_{J_1}\). We then fixed \(\sigma_{J_1} = 0.09\) and calculated
the predicted growth rate of our 12 populations.

@@

Third, we defined a version of the model with demographic and
environmental stochasticity, where environmental stochasticity was
represented by among-year variability in \(\sigma_{J_1}\). We used this
model to simulate a one-time introduction of 40 translocated adult
frogs. We ran this simulation 1000 times for each population and
computed the probability of a population becoming extinct after 50 years
given the observed parameter values and environmental stochasticity in
\(\sigma_{J_1}\). We varied the mean recruitment probability
\(\sigma_{J_1}\) from 0 and 0.25 and drew values of \(\sigma_{J_1}\)
each year from a beta distribution with a dispersion parameter of
\(\phi = 2\) (when \(\sigma_{J_1} = 0.5\) and \(\phi = 2\) the beta
distribution is uniform between 0 and 1). Using different values of
\(\phi\) does not qualitatively change the existence of distinct
extinction dynamics between populations with \(\sigma_{A_R} < 0.5\) and
those with \(\sigma_{A_R} > 0.5\). However, increasing yearly
variability in \(\sigma_{J_1}\) increases extinction risk for all
populations. For example, if we set \(\phi = 0.001\), such that in a
given year essentially either all year 1 juveniles survive or all of
them die, populations with \(\sigma_{A_R} > 0.5\) need to have
\(\sigma_{J_1}\) greater than 0.2 to have a 50-year extinction
probability of less 50\%. Because we do not pit tag juveniles, we do not
have CMR estimates for \(\sigma_{J_1}\) or \(\phi\). However, based on
qualitative and semi-quantitative field observations over 25 years, a
value of \(\sigma_{J_1} = 0.25\) in the presence of Bd is probably a
reasonable estimate for many populations. Thus, we expect our model
predictions to be conservative with regards to population recovery.

@@

To gain insights into the role of evolution in the development of
resistance by MYL frogs, we compared frog genomes sampled in naive
versus recovering populations. Comparing populations with different
infection histories allowed larger sample sizes and replication across
the landscape. The alternative approach of comparing samples from the
same populations before and after Bd exposure isn't feasible in this
system because Bd arrived in most MYL frog populations decades ago and
population persistence/recovery is rare and unpredictable. As a result,
samples from recovering populations collected from before and after Bd
exposure are not available and are unlikely to be available in the
future.

Our study design, in which we compared frog genomes in naive and
recovering populations, required sampling populations across the range
of MYL frogs in the southern Sierra Nevada. This is due to the fact that
very few MYL frog populations remain in the naive state, and those that
do are scattered across a wide latitudinal range, from Yosemite National
Park in the north to southern Kings Canyon National Park in south. To
minimize potential confounding effects caused by known variation in frog
genotypes across latitude \citep{byrne2023}, we selected sampling sites
such that both population types were represented across similar
latitudinal ranges (Fig. 1).

@@

In \textbf{Results-Frog evolution in response to Bd}, we describe the
stringent set of outlier variants (identified using a
Bonferroni-corrected p-value of 0.01). A liberal set of outlier
variants, identified using a Bonferroni-corrected p-value of 0.05,
included 38 outliers (35 SNPs and 3 INDELS) from 30 distinct genes
across 16 contigs. We used this liberal set to determine if any GO
biological functions, molecular functions, or cellular processes were
overrepresented. To do this, we retrieved the BLAST hits and mapped GO
terms for each gene in our targeted transcriptome. We then conducted a
statistical overrepresentation test (Fisher's exact test) using Blast2GO
\citep{conesa2005} to compare the 30 unique outlier genes to the
complete set of genes in our target transcriptome. We repeated this
process for the set of 33 genes located in the
\emph{F\textsubscript{ST}} and \(\pi_{diff}\) splined windows.

@@

\caption{\label{fig-compare_surv_probs}Comparison of average yearly
adult survival probabilities for adults translocated to each of 3 sites
versus adults that were naturally recruited at each site (as a result of
reproduction by translocated frogs). In contrast to
Fig. 3, these are not survival
probabilities from the first year following translocation, but instead
represent averaged survival probabilities across multiple years and
cohorts. Points are median estimates and error bars give the 95\%
uncertainty intervals around the estimates, accounting for yearly
variation in survival probabilities. All estimates were derived using
the mrmr package, and the methods for calculation are described in
\textbf{Supporting Information - Population viability modeling --
Estimating model parameters}.}

@@

\caption{\label{fig-viability-supp}Sensitivity analysis of the
stage-structured MYL frog model. Elasticity of \(\lambda\) with changes
in four parameters: \(\sigma_{A_R}\) (yearly survival probability of
naturally recruited adults), \emph{F (}number of eggs produced by a
female frog in a year that successfully hatch), \(\sigma_{J_1}\) (yearly
probability of survival of year 1 juveniles that also affects
recruitment), and \(\sigma_{J_2}\) (yearly probability of survival and
recruitment of year 2 juveniles). Elasticity is calculated at the
default parameter values for each population and \(\sigma_{J_1}\) =
0.09.}

@@

\caption{\label{fig-selectionresults}Results from the analysis of
individual variants, showing putative signatures of selection in
recovering MYL frog populations. (A) PCA calculated from binary SNPs
showing the genomic relationship of samples. Numeric labels and colors
match those in Fig. 1A. Populations 1-7 are
\emph{R. sierrae} and populations 8 and 9 are \emph{R. muscosa}. (B)
qqplot showing observed and expected p-values for 148,307 SNPs and
INDELS. Dashed line shows p-value that identifies outliers. (C)
Manhattan plot showing p-value for each SNP. SNPs are sorted by genomic
position and contigs are sorted by size. Red line shows p-value that
identifies outliers. Outlier SNPs above this threshold are highlighted
and labeled. Bold labels indicate the presence of at least one
non-synonymous SNP in that gene.}

@@

\caption{\label{fig-violinplot-heterozy}Violin plots showing individual
heterozygosity for the Bd-naive and recovering populations included in
the frog evolution study. Individual data points are represented by
their corresponding site number (from
Fig. 1).}

@@

\caption{\label{fig-boxplot-genomewide-pi-by-pop}For each study
population in the frog evolution study (from
Fig. 1), boxplots showing nucleotide
diversity (\(\pi\)) within 100kb sliding windows along the genome. The
y-axis has been log\textsubscript{10}-transformed for display purposes.
Sites are color-coded as ``Bd-naive'' or ``recovering'', and vertical
dashed lines show the genetic breaks between frog populations as
described in Figure~\ref{fig-selectionresults} A). Within the genetic
clusters, mean \(\pi\) is significantly different between sites (p
\textless0.001 Wilcoxon rank-sum test).}

@@

\caption{\label{fig-boxplot-pi-by-windowpop}For each of the 9 outlier
windows identified by the overlapping splined windows for FST and
\$\textbackslash pi\$, boxplots showing average \$\textbackslash pi\$
for naive and recovering populations. The corresponding gene annotations
for each window are as follows: (1) C6, C7, (2) DDX10, ZBTB24, (3)
SULTR-like, TRAF3IP2, VGLL3, EXOC1, (4) FLOT1, TUBB, MDC1, CCHCR1,
TCF19, HSP70, LSM2, VARS1, (5) GCC2, CFAP251, PEG10, (6) ERO1A, GVINP1,
(7) PPP1R12A, TSPAN4, PAWR, MFRP, MAX, PPP6R3, (8) C6H5ORF22, PKS6,
BSPRY, MPV17, and (9) CAD, ATRAID, GPN1.}

@@

\hypertarget{tbl-param_values}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3611}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2639}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3750}}@{}}
\caption{\label{tbl-param_values}Description and values of parameters
used in the model. All survival probabilities are in the presence of the
fungal pathogen Bd.}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Parameter}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Value}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Source}
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Parameter}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Value}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Source}
\end{minipage} \\
\midrule()
\endhead
\(\sigma_{L_1}\), Yearly survival probability of year 1 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{L_2}\), Yearly survival probability of year 2 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{L_3}\), Yearly survival probability of year 3 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{J_1}\), Yearly survival probability of year 1 juveniles &
Varies yearly & Varies. Bounds estimated from field data, observations,
natural history knowledge \\
\(\sigma_{J_2}\), Yearly survival probability of year 2 juveniles & 0.5
& Estimated from field data, observations, natural history knowledge \\
\(\sigma_{A_R}\), Yearly survival probability of naturally recruited
adults & Varies by population & Estimated from CMR studies \\
\(\sigma_{A_T}\), Yearly survival probability of translocated adults &
Varies by population & Estimated from CMR studies \\
\(p_{L_1}\), Probability of a year 1 tadpoles remaining as a tadpoles &
1 & Estimated from field data, observations, natural history
knowledge \\
\(p_{L_2}\), Probability of a year 2 tadpoles remaining as a tadpoles &
0.25 & Estimated from field data, observations, natural history
knowledge \\
\(p_{J_1}\), Probability of a year 1 juvenile remaining as a juvenile &
0.25 & Estimated from field data, observations, natural history
knowledge \\
\(p_F\), Probability of a adult female reproducing in a year & 0.5 &
Could be as high at 1, based on field observations \\
\(F\), Number of surviving eggs produced by an adult female & 100 & From
observations of captive frogs \\
\bottomrule()
\end{longtable}

>>>>

\hypertarget{laboratory-methods}{%
\subsection{Laboratory methods}\label{laboratory-methods}}

@@

The state transition matrix \(\Psi_{t, i}\) contains the probabilities
of individual \(i\) transitioning from state \(u_{i, t}\) (rows) to
\(u_{i, t+1}\) (columns) between primary period \(t\) and \(t+1\). For
non-introduced (i.e., naturally recruited) individuals, this matrix is
given by:

@@

To complete the specification of the Bayesian model, we specify priors
for all unknown parameters. The recruitment parameter priors were
specified as follows:

@@

\hypertarget{population-viability-modeling-1}{%
\section{Population viability
modeling}\label{population-viability-modeling-1}}

\hypertarget{incorporating-yearly-variability-in-vital-rates}{%
\subsection{Incorporating yearly variability in vital
rates}\label{incorporating-yearly-variability-in-vital-rates}}

We computed yearly survival probabilities for translocated adults
\(\sigma_{A_T}\) and naturally recruited adults \(\sigma_{A_R}\) from
the posterior distribution of individual state trajectories derived from
mrmr CMR models. Although we observed yearly variability in adult
survival within a population, the magnitude of this variability was
small compared to among-population variability
(Fig. 2). Thus, we did not include
yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in
the successful recruitment of adults, greater than what we would expect
from Poisson variability around a mean value. Therefore, we allowed for
yearly variability in the probability of year-1 juvenile survival and
recruitment (additional details provided in \textbf{Estimating model
parameters} below). We also could have included environmental
stochasticity in year-2 juvenile survival and recruitment
\(\sigma_{J_2}\), but our elasticity analysis (\textbf{Supporting
Information - Population viability modeling - Model analysis and
simulation}) showed that this parameter had little effect on host growth
rate relative to \(\sigma_{J_1}\) (Figure~\ref{fig-viability-supp}).

\hypertarget{estimating-model-parameters}{%
\subsection{Estimating model
parameters}\label{estimating-model-parameters}}

The baseline parameter values for the model and how they were estimated
are given in Table~\ref{tbl-param_values}. Parameters \(\sigma_{A_T}\)
and \(\sigma_{A_R}\) were extracted directly from our CMR models (see
\textbf{Materials and Methods - Frog populaton recovery - Estimation of
frog survival and abundance} and \textbf{Supporting Information - Frog
population recovery - CMR model structure} for details). For populations
where we had a sufficient number of PIT-tagged, naturally-recruited
adults, we observed that \(\sigma_{A_T}\) and \(\sigma_{A_R}\) could be
notably different, with \(\sigma_{A_R} > \sigma_{A_T}\)
(Figure~\ref{fig-compare_surv_probs}). For populations lacking
sufficient numbers of naturally-recruited adults, we were unable to
directly estimate \(\sigma_{A_R}\), and instead set
\(\sigma_{A_R} = \sigma_{A_T}\).

To estimate the \(\sigma_{A_R}\), we used the posterior distribution of
predicted true states for naturally-recruited individuals (1=not
recruited, 2=alive, 3=dead, as described in \textbf{Supporting
Information - Frog population recovery - CMR model structure}), then
calculated the posterior probability of individuals surviving between
consecutive primary periods, conditional on being alive in the first
primary period (e.g., given a value of 2 (alive) in the first primary
period, how often was the value still 2 (alive) in the next primary
period compared to 3 (dead)?) . This yielded posterior distributions for
survival probabilities between primary periods. However, because the
time interval between primary periods differed, the survival
probabilities between different consecutive primary periods were not
directly comparable. To address this, we converted the survival
probabilities between each consecutive primary period to per day death
rates, propagating the uncertainty from the posterior distributions. We
then took a weighted average of these death rates, weighted by the time
interval between primary periods, to get the average per day death rate
over the entire CMR survey. We converted this per day death rate \(d\)
back to a yearly survival probability using
\(\exp(-d \times 365 \text{ days})\). We used the same procedure for
\(\sigma_{A_T}\) such that our estimates of average yearly survival
probability were comparable between \(\sigma_{A_R}\) and
\(\sigma_{A_T}\).

\hypertarget{model-analysis-and-simulation}{%
\subsection{Model analysis and
simulation}\label{model-analysis-and-simulation}}

We performed four analyses on our model. First, we considered a
deterministic version of our model with no yearly heterogeneity in
year-1 juvenile survival and recruitment probability \(\sigma_{J_1}\),
and calculated the predicted long-run growth rate \(\lambda\) of a
population for different values of \(\sigma_{A_R}\) and
\(\sigma_{J_1}\). We then fixed \(\sigma_{J_1} = 0.09\) and calculated
the predicted growth rate of our 12 populations.

@@

Third, we defined a version of the model with demographic and
environmental stochasticity, where environmental stochasticity was
represented by among-year variability in \(\sigma_{J_1}\). We used this
model to simulate a one-time introduction of 40 translocated adult
frogs. We ran this simulation 1000 times for each population and
computed the probability of a population becoming extinct after 50 years
given the observed parameter values and environmental stochasticity in
\(\sigma_{J_1}\). We varied the mean recruitment probability
\(\sigma_{J_1}\) from 0 and 0.25 and drew values of \(\sigma_{J_1}\)
each year from a beta distribution with a dispersion parameter of
\(\phi = 2\) (when \(\sigma_{J_1} = 0.5\) and \(\phi = 2\) the beta
distribution is uniform between 0 and 1). Using different values of
\(\phi\) does not qualitatively change the existence of distinct
extinction dynamics between populations with \(\sigma_{A_R} < 0.5\) and
those with \(\sigma_{A_R} > 0.5\). However, increasing yearly
variability in \(\sigma_{J_1}\) increases extinction risk for all
populations. For example, if we set \(\phi = 0.001\), such that in a
given year essentially either all year-1 juveniles survive or all of
them die, populations with \(\sigma_{A_R} > 0.5\) need to have
\(\sigma_{J_1}\) greater than 0.2 to have a 50-year extinction
probability of less 50\%. Because we do not pit tag juveniles, we do not
have CMR estimates for \(\sigma_{J_1}\) or \(\phi\). However, based on
qualitative and semi-quantitative field observations over 25 years, a
value of \(\sigma_{J_1} = 0.25\) in the presence of Bd is probably a
reasonable estimate for many populations. Thus, we expect our model
predictions to be conservative with regards to population recovery.

@@

To gain insights into the role of evolution in the development of
resistance by MYL frogs, we compared frog exomes sampled in naive versus
recovering populations. Comparing populations with different infection
histories allowed larger sample sizes and replication across the
landscape. The alternative approach of comparing samples from the same
populations before and after Bd exposure isn't feasible in this system
because Bd arrived in most MYL frog populations decades ago and
population persistence/recovery is rare and unpredictable. As a result,
samples from recovering populations collected before and after Bd
exposure are not available and are unlikely to be available in the
future.

Our study design, in which we compared frog genomes in naive and
recovering populations, required sampling populations across the range
of MYL frogs in the southern Sierra Nevada. This is due to the fact that
very few MYL frog populations remain in the naive state, and those that
do are scattered across a wide latitudinal range, from Yosemite National
Park in the north to southern Kings Canyon National Park in south. To
minimize potential confounding effects caused by known variation in frog
genotypes across latitude \citep{byrne2023}, we selected sampling sites
such that both population types were represented across similar
latitudinal ranges (Fig. 5).

@@

In \textbf{Results-Frog evolution in response to Bd}, we describe the
stringent set of outlier variants (identified using a
Bonferroni-corrected p-value of 0.01). A liberal set of outlier
variants, identified using a Bonferroni-corrected p-value of 0.05,
included 38 outliers (35 SNPs and 3 INDELS) from 30 distinct genes
across 16 contigs. We used this liberal set to determine if any GO
biological functions, molecular functions, or cellular processes were
overrepresented. To do this, we retrieved the BLAST hits and mapped GO
terms for each gene in our targeted transcriptome. We then conducted a
statistical overrepresentation test (Fisher's exact test) using Blast2GO
\citep{conesa2005} to compare the 30 unique outlier genes to the
complete set of genes in our target transcriptome. We repeated this
process for the set of 35 genes located in the 9 shared regions of the
\emph{F\textsubscript{ST}} and \(\pi_{diff}\) splined windows.

@@

\caption{\label{fig-compare_surv_probs}Comparison of average yearly
adult survival probabilities for adults translocated to each of 3 sites
versus adults that were naturally recruited at each site (as a result of
reproduction by translocated frogs). In contrast to
Fig. 2, these are not survival
probabilities from the first year following translocation, but instead
represent averaged survival probabilities across multiple years and
cohorts. Points are median estimates and error bars give the 95\%
uncertainty intervals around the estimates, accounting for yearly
variation in survival probabilities. All estimates were derived using
the mrmr package, and the methods for calculation are described in
\textbf{Supporting Information - Population viability modeling -
Estimating model parameters}.}

@@

\caption{\label{fig-viability-supp}Sensitivity analysis of the
stage-structured MYL frog model. Elasticity of \(\lambda\) with changes
in four parameters: \(\sigma_{A_R}\) (yearly survival probability of
naturally recruited adults), \emph{F (}number of eggs produced by a
female frog in a year that successfully hatch), \(\sigma_{J_1}\) (yearly
probability of survival of year-1 juveniles that also affects
recruitment), and \(\sigma_{J_2}\) (yearly probability of survival and
recruitment of year-2 juveniles). Elasticity is calculated at the
default parameter values for each population and \(\sigma_{J_1}\) =
0.09.}

@@

\caption{\label{fig-selectionresults}Results from the analysis of
individual variants, showing putative signatures of selection in
recovering MYL frog populations. (A) PCA calculated from binary SNPs
showing the genomic relationship of samples. Numeric labels and colors
match those in Fig. 5. Populations 1-7 are
\emph{R. sierrae} and populations 8 and 9 are \emph{R. muscosa}. (B)
qqplot showing observed and expected p-values for 148,307 SNPs and
INDELS. Dashed line shows p-value that identifies outliers. (C)
Manhattan plot showing p-value for each SNP. SNPs are sorted by genomic
position and contigs are sorted by size. Red line shows p-value that
identifies outliers. Outlier SNPs above this threshold are highlighted
and labeled. Bold labels indicate the presence of at least one
non-synonymous SNP in that gene.}

@@

\caption{\label{fig-violinplot-heterozy}Violin plots showing individual
heterozygosity for the Bd-naive and recovering populations included in
the frog evolution study. Individual data points are represented by
their corresponding site number (from
Fig. 5).}

@@

\caption{\label{fig-boxplot-genomewide-pi-by-pop}For each study
population in the frog evolution study (from
Fig. 5), boxplots showing nucleotide
diversity (\(\pi\)) within 100kb sliding windows along the genome. The
y-axis has been log\textsubscript{10}-transformed for display purposes.
Sites are color-coded as ``Bd-naive'' or ``recovering'', and vertical
dashed lines show the genetic breaks between frog populations as
described in Figure~\ref{fig-selectionresults} A).}

@@

\caption{\label{fig-boxplot-pi-by-windowpop}For each of the 9 outlier
windows identified by the overlapping splined windows for FST and
\(\pi\), boxplots showing average \(\pi\) for naive and recovering
populations. The corresponding gene annotations for each window are as
follows: (1) C6, C7, (2) DDX10, ZBTB24, (3) SULTR-like, TRAF3IP2, VGLL3,
EXOC1, (4) FLOT1, TUBB, MDC1, CCHCR1, TCF19, HSP70, LSM2, VARS1, (5)
GCC2, CFAP251, PEG10, (6) ERO1A, GVINP1, (7) PPP1R12A, TSPAN4, PAWR,
MFRP, MAX, PPP6R3, (8) C6H5ORF22, PKS6, BSPRY, MPV17, and (9) CAD,
ATRAID, GPN1.}

@@

\hypertarget{tbl-param_values}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3611}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2639}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3750}}@{}}
\caption{\label{tbl-param_values}Description and values of parameters
used in the model. All survival probabilities are in the presence of the
fungal pathogen Bd.}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Parameter}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Value}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Source}
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Parameter}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Value}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Source}
\end{minipage} \\
\midrule()
\endhead
\(\sigma_{L_1}\), Yearly survival probability of year-1 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{L_2}\), Yearly survival probability of year-2 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{L_3}\), Yearly survival probability of year-3 tadpoles & 0.7 &
Estimated from field data, observations, natural history knowledge \\
\(\sigma_{J_1}\), Yearly survival probability of year-1 juveniles &
Varies yearly & Varies. Bounds estimated from field data, observations,
natural history knowledge \\
\(\sigma_{J_2}\), Yearly survival probability of year-2 juveniles & 0.5
& Estimated from field data, observations, natural history knowledge \\
\(\sigma_{A_R}\), Yearly survival probability of naturally recruited
adults & Varies by population & Estimated from CMR studies \\
\(\sigma_{A_T}\), Yearly survival probability of translocated adults &
Varies by population & Estimated from CMR studies \\
\(p_{L_1}\), Probability of a year-1 tadpoles remaining as a tadpoles &
1 & Estimated from field data, observations, natural history
knowledge \\
\(p_{L_2}\), Probability of a year-2 tadpoles remaining as a tadpoles &
0.25 & Estimated from field data, observations, natural history
knowledge \\
\(p_{J_1}\), Probability of a year-1 juvenile remaining as a juvenile &
0.25 & Estimated from field data, observations, natural history
knowledge \\
\(p_F\), Probability of a adult female reproducing in a year & 0.5 &
Could be as high at 1, based on field observations \\
\(F\), Number of surviving eggs produced by an adult female & 100 & From
observations of captive frogs \\
\bottomrule()
\end{longtable}
